[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-02-24 analysis/paper.Rmd
Updated rmd

In this replication paper, three artifacts from [@data] were reproduced. The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear models created.

@@

The dataset from gssr contained a larger time interval than the original paper, it was filtered back to match the original intervals. Only years prior to 2008 are used in both analyses. This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the total column to the GSS data using year as the key.

@@

Figure 3 in the original publication plots mean happiness of respondentsover time. This data is categorized into 3 groups by racial identity: White, Black and Other. Best-fitting regression lines are included to display the trend of mean happiness for the 3 populations.

>>>>

In this replication paper, three artifacts from [@data] were reproduced. The first artifact, Figure 3., plots the mean happiness by year and race, the second, Table 1, shows the linear regression model's coefficients and the third, Table 2, shows the correlation coefficients of the different independent variables used in the linear mixed-effect models created.

@@

The dataset from gssr contained a larger time interval than the original paper. It was filtered back to match the original interval. Only years prior to 2008 are used in both analyses. This dataset was also merged with the original US Census Bureau data found in Gini_families.csv[@data] by appending the "total" column to the GSS data using "year" as the join key.

@@

Figure 3 in the original publication plots mean happiness of respondents over time. This data is categorized into 3 groups by racial identity: White, Black and Other. Best-fitting regression lines are included to display the trend of mean happiness for the 3 populations.
